---
title: "Multiple Linear Regression Using R"
output: html_notebook
---

Data Preparation
```{r}
data<-read.csv("D:\\Browser downloads\\VIT Downloads\\Other Downloads\\Assignments\\HousePricePrediction.csv")
head(data)
```
```{r}
dim(data)
```
Data Cleaning

Create a user defined to find the missing values
```{r}
getMissingValues <- function(data){
  missing_values <- colSums(is.na(data))
  sorted_missing_values <- sort(missing_values, decreasing = TRUE)
  for(col_name in names(sorted_missing_values)) {
    cat("column: ", col_name, "\tMissing Values:",sorted_missing_values[col_name],"\n")
  }
}
getMissingValues(data)
```
Omit the missing values
```{r}
data <- na.omit(data)
sum(is.na(data))
```
Since Id Field has no impact on the house price we remove it.
```{r}
data <- subset(data, select = -Id)
colnames(data)
```
Performing Label Encoding
```{r}
data$MSZoning <- as.numeric(factor(data$MSZoning))
data$LotConfig <- as.numeric(factor(data$LotConfig))
data$BldgType <- as.numeric(factor(data$BldgType))
data$Exterior1st <- as.numeric(factor(data$Exterior1st))
subset(data, select = c('MSZoning', 'LotConfig', 'BldgType', 'Exterior1st'))
```
Correlation Plot
```{r}
library(ggplot2)
library(ggcorrplot)

ggcorrplot(cor(data), method = "square", hc.order = TRUE,lab = TRUE, colors = c("purple","skyblue","brown"), outline.color = "red")
```
```{r}
library(ggplot2)

ggplot(data, aes(x = SalePrice))+
  geom_histogram(binwidth = 50000, fill="purple", color='red')+
  labs(title = "Distribution of Price", x ="Price")+
  theme_minimal()
  
```
Plotting the Regression Line using "lm" function
```{r}
ggplot(data, aes(x = LotArea, y = SalePrice))+
  geom_point(color = "orange")+
  theme_minimal()+
  labs(title = "ScatterPlot: Lot area vs. Sale Price", x= "Lotarea", y="Saleprice")+
  geom_smooth(method = lm)

```
Splitting data into train and test
```{r}
set.seed(123)
train_proportion <- 0.8
train_indices <- sample(1:nrow(data),size = round(train_proportion*nrow(data)))

train_Data <- data[train_indices,]
test_Data <- data[-train_indices,]

dim(test_Data)
dim(train_Data)
```
Train a Multiple Linear Regression Model on the train data
```{r}
model = lm(SalePrice ~ ., data=train_Data)
summary(model)
```
Model Prediction:
```{r}
predictions <- predict(model, newdata = test_Data)
head(predictions)
```
Predicting on Sample Data:
```{r}
test_case <- data.frame(MSSubClass = 60,MSZoning = 4,LotArea = 8450,
                        LotConfig = 5, BldgType = 1, OverallCond = 5,
                        YearBuilt = 2003, YearRemodAdd = 2003,
                        Exterior1st = 13, BsmtFinSF2 = 0,TotalBsmtSF = 856)
predicted_price <- predict(model, newdata = test_case)
print(predicted_price)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
